E. coli Testing: Safeguarding Public Health

### 2024-09-27 paper/paper.qmd
Rename starter_folder-main/paper/paper.qmd to paper/paper.qmd

The number of E.coli in freshwater is determined by counting the number of yellow and yellow-brown colonies that grow after placing a 0.45-micron filter on m-TEC medium and incubating it at 35.0ºC for 22-24 hours. The water quality standard for E.coli in Ontario and federally is 200 E.coli per 100 milliliters of water, while Toronto beach water quality standard is 100 E.coli per 100 milliliters of water. This article utilizes 22,000 data points collected by government departments from June to September from 2007 to 2024 to assess whether the E.coli is much more than the Toronto water quality standard. Meanwhile, it try to prove if the E.coli is influenced by the change of time and site location.

@@

## Raw Data
The data used in this paper is from Open Data Toronto and download by the @citeopendatapkg. The @citedata is used to analyze whether the E.coli value in the beach during June and September is satisfy for people to swim. All the data analysis is through the @citeR and the completed by following packages：@citetidyverse, @citedplyr, @citejanitor, @citeggplot2, @citehere, @citekableExtra and @citeknitr.
The dataset is published by Toronto Public Health and is part of The Beach Water Sampling Program, which collects E. coli values from two different beaches. The data is updated daily, and the data used for this analysis spans from June 3, 2007, to September 8, 2024. The raw dataset contains 21,882 water quality samples testing for E.coli concentrations. The dataset also includes beach itendifiers, names, sample site names, collection dates for each sample, and geographic coordinates (latitude and longitude).

>>>>

The number of E.coli in freshwater is determined by counting the number of yellow and yellow-brown colonies that grow after placing a 0.45-micron filter on m-TEC medium and incubating it at 35.0ºC for 22-24 hours @citebacteria. The water quality standard for E.coli in Ontario and federally is 200 E.coli per 100 milliliters of water, while Toronto beach water quality standard is 100 E.coli per 100 milliliters of water @citewaterquality. This article utilizes 22,000 data points collected by government departments from June to September from 2007 to 2024 to assess whether the E.coli is much more than the Toronto water quality standard. Meanwhile, it try to prove if the E.coli is influenced by the change of time and site location.

@@

## Raw Data
The data used in this paper is from Open Data Toronto and download by the @citeopendatapkg. The @citedata is used to analyze whether the E.coli value in the beach during June and September is satisfy for people to swim. All the data analysis is through the @citeR, the templete from @citeRohan and the completed by following packages：@citetidyverse, @citedplyr, @citejanitor, @citeggplot2, @citehere, @citekableExtra and @citeknitr.
The dataset is published by Toronto Public Health and is part of The Beach Water Sampling Program, which collects E. coli values from two different beaches. The data is updated daily, and the data used for this analysis spans from June 3, 2007, to September 8, 2024. The raw dataset contains 21,882 water quality samples testing for E.coli concentrations. The dataset also includes beach itendifiers, names, sample site names, collection dates for each sample, and geographic coordinates (latitude and longitude).
